\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-17 paper/main.tex
added CDL bibliography as a submodule

Computational researchers and other programmers have developed a broad
set of approaches and tools to facilitate code sharing and
reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
extreme, simply distributing a set of Python scripts (\texttt{.py} files) may
enable others to use or gain insights into the relevant work. Because
Python is installed by default on most modern operating systems, for
some projects, this may be sufficient. Another popular approach
entails creating Jupyter
notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
code, and embedded media. Notebooks may call or import external
scripts or libraries---even intersperse snippets of other programming
or markup lang\-uages---in order to provide a more compact and readable
experience for users. Both of these systems (Python scripts and
notebooks) provide a convenient means of sharing code, with the
caveat that they do not specify the computing environment in which the
code is executed. Therefore the functionality of code shared using
these systems cannot be guaranteed across different users or setups.

@@

%---------------------------------------------------- BIBLIOGRAPHY -----------------------------------------------------
\bibliographystyle{elsarticle-num}
\bibliography{cdl}

>>>>

Computational researchers and other programmers have de\-vel\-oped a broad
set of approaches and tools to facilitate code sharing and
reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
extreme, simply distributing a set of Python scripts (\texttt{.py} files) may
enable others to use or gain insights into the relevant work. Because
Python is installed by default on most modern operating systems, for
some projects, this may be sufficient. Another popular approach
entails creating Jupyter
notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
code, and embedded media. Notebooks may call or import external
scripts or libraries---even intersperse snippets of other programming
or markup lang\-uages---in order to provide a more compact and readable
experience for users. Both of these systems (Python scripts and
notebooks) provide a convenient means of sharing code, with the
caveat that they do not specify the computing environment in which the
code is executed. Therefore the functionality of code shared using
these systems cannot be guaranteed across different users or setups.

@@

%---------------------------------------------------- BIBLIOGRAPHY -----------------------------------------------------
\bibliographystyle{elsarticle-num}
\bibliography{CDL-bibliography/cdl}
